STA610 Case Study 1 Team 4 Report

### 2021-03-21 STA 610 Case Study 1 Report_Team 4.Rmd
Perform nested model tests to decide on dropping variables

Now let's investigate dropping various

>>>>

Now let's investigate dropping various fixed effects and see results of our hypothesis tests:

```{r}
# Test date_num
test <- anova(mod_s,
      lmer(data=df, log_ppm ~ (1 |state) + date_quarter + dose_per_mg + bulk_purchase + Primary_Reason + source, REML=F))
print(test$`Pr(>Chisq)`)  # Drop date_num

# Test date_quarter
test <- anova(lmer(data=df, log_ppm ~ (1 |state) + date_quarter + dose_per_mg + 
                    bulk_purchase + Primary_Reason + source, REML=F),
      lmer(data=df, log_ppm ~ (1 |state) + dose_per_mg + bulk_purchase + Primary_Reason + source, REML=F))
print(test$`Pr(>Chisq)`) # drop date_quarter

# Test dose_per_mg
test <- anova(lmer(data=df, log_ppm ~ (1 |state) + dose_per_mg + bulk_purchase + Primary_Reason + source, REML=F),
      lmer(data=df, log_ppm ~ (1 |state) + bulk_purchase + Primary_Reason + source, REML=F))
print(test$`Pr(>Chisq)`)  # Don't drop dose_per_mg

# Test bulk purchase
test <- anova(lmer(data=df, log_ppm ~ (1 |state) + dose_per_mg + bulk_purchase + Primary_Reason + source, REML=F),
      lmer(data=df, log_ppm ~ (1 |state) + dose_per_mg + Primary_Reason + source, REML=F))
print(test$`Pr(>Chisq)`) # Don't drop bulk_purchase

# Test primary reason
test <- anova(lmer(data=df, log_ppm ~ (1 |state) + dose_per_mg + bulk_purchase + Primary_Reason + source, REML=F),
      lmer(data=df, log_ppm ~ (1 |state) + dose_per_mg + bulk_purchase + source, REML=F))
print(test$`Pr(>Chisq)`) # Don't drop Primary_reason

# Test source
test <- anova(lmer(data=df, log_ppm ~ (1 |state) + dose_per_mg + bulk_purchase + source, REML=F),
      lmer(data=df, log_ppm ~ (1 |state) + dose_per_mg + bulk_purchase, REML=F))
print(test$`Pr(>Chisq)`) # Don't drop source
```

Thus these results suggest we want to drop
